### 2022-02-08 symposium.tex
Type and Null Safety for Regexes typos

\noindent
The result of that type-level computation takes the form of a Scala tuple with |String| and |Option[String]| element, depending of the optionality analysis.

@@

\noindent
The |Length| and |CharAt| types are special-cased by the compiler: when their first argument is a literal singleton string, the compiler evaluates those types via their corresponding term-level implementation.
Similarly, the |+| type from |compiletime.ops.int| allows us to manipulate integer just like we would at the term level.
The |EmptyTuple| and |*:| are Scala~3's new generic representation of tuples.
Those types remove the need for heterogeneous lists and allow us to manipulate tuples directly.

@@

Our first implementation of |Compile| treats every opening parenthesis as the start of a capture group, which does not do honor to the syntax of Java's regular expression.
Indeed, Java also support several other special constructs which start with an opening parethesis, such as non-capturing groups, |(?:X)|, lookaheads, |(?=X)| \& |(?!X)|, and lookbehinds, |(?<=X)| \& |(?<!X)|, and must all be discriminated from named and unnamed-capturing groups, |(?<name>X)| \& |(X)|.

>>>>

\noindent
The result of that type-level computation takes the form of a Scala tuple with |String| and |Option[String]| elements, depending of the optionality analysis.

@@

\noindent
The |Length| and |CharAt| types are special-cased by the compiler: when their first argument is a literal singleton string, the compiler evaluates those types via their corresponding term-level implementation.
Similarly, the |+| type from |compiletime.ops.int| allows us to manipulate integers just like we would at the term level.
The |EmptyTuple| and |*:| are Scala~3's new generic representation of tuples.
Those types remove the need for heterogeneous lists and allow us to manipulate tuples directly.

@@

Our first implementation of |Compile| treats every opening parenthesis as the start of a capture group, which does not do honor to the syntax of Java's regular expression.
Indeed, Java also supports several other special constructs which start with an opening parethesis, such as non-capturing groups, |(?:X)|, lookaheads, |(?=X)| \& |(?!X)|, and lookbehinds, |(?<=X)| \& |(?<!X)|, and must all be discriminated from named and unnamed-capturing groups, |(?<name>X)| \& |(X)|.
